Selecting similar behaving group of customers to check clustering methodology

### 2021-10-18 check_work.Rmd
adding new simulation files

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk(here('script/smart_meter.R'))
```

```{r mytheme}
theme_validation <- function() {
  theme_bw() +
      theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 1)),
    plot.margin = margin(0, 0, 0, 0, "cm"),
    axis.title.y = element_blank(),
    #axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
      legend.position = "bottom"
    )
}

theme_characterisation <- function() {

  theme_bw() + # seeting theme
    theme(strip.text = element_text(size = 7,
                                    margin = margin(b = 0, t = 0))) + # narrow facet space
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + # no axis ticks 
  theme(panel.spacing =unit(0, "lines")) +  # to ensure no gap between facets
    theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + # rotate the x-axis text
    theme(legend.position = "bottom")+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  theme(axis.text.x = element_text(size=5))
}
```

```{r anchor}
anchor1 <- 11156027
anchor2 <- 10420683
anchor3 <- 8629763
anchor4 <-

```{r data-pick}

@@

hod <- read_rds(here("data/dist_gran_hod_356cust_robust.rds")) 
distance <- wkndwday %>% 
  left_join(moy, by = c("item1", "item2")) %>% 
  left_join(hod, by = c("item1", "item2")) %>% 
  rename("wkndwday" ="distance.x",
         "moy" = "distance.y",
         "hod" = "distance") %>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

total_distance <- distance %>% 
  mutate(total = hod)
  #mutate(total = wkndwday/2 + moy/12 + hod/24)

# 8454221 10420689 1001 8454221 10018298 10420689 9393696
data_pick_one <- total_distance %>% filter(item1 %in% 
                            c(11156027)|item2 %in% 
                            c(11156027) ) %>% 
  #group_by(item1) %>%
  arrange(total) %>% 
  head(5) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

#11013154  8181071 11048034
data_pick_two <- total_distance %>% filter(item1 %in% 
                            c(10420683)|item2 %in% 
                            c(10420683)) %>% group_by(item1) %>% arrange(total) %>% head(5)%>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

data_pick_three <- total_distance %>% filter(item1 %in% 
                              c(11013154)) %>%
  #group_by(item1) %>%
  arrange(total) %>% head(5)%>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

# 8653709
data_pick_four <- total_distance %>% filter(item1 %in%
                            c(8629763)|item2 %in% 
                            c(8629763)) %>% 
  #group_by(item1) %>% 
  arrange(total) %>% head(5)%>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

# c(11013154, 8495194, 8627007,10109182,10677705,8952846)

data_pick_cust <- bind_rows(
unique(c(data_pick_one$item1,data_pick_one$item2)) %>% as_tibble(),    unique(c(data_pick_two$item1,data_pick_two$item2)) %>% as_tibble(), 
c(11013154, 9345642, 8328008, 8636035,8627007,8454235) %>% as_tibble(),
unique(c(data_pick_four$item1,data_pick_four$item2)) %>% as_tibble(),
.id = "design")

@@

data_pick <- read_rds(here::here("data/elec_nogap_2013_clean_356cust.rds"))%>%
  filter(customer_id %in% data_pick_cust$value) %>% 
  gracsr::scale_gran( method = "robust", response = "general_supply_kwh")

@@

group <- f %>% hclust (method = "ward.D") %>% cutree(k=4)

@@

mds  = cmdscale(f)
rownames(mds) = id
colnames(mds) = c("mds1", "mds2")

# ggplot(data = mds %>% as_tibble() %>% mutate(group = cluster_result$group), 
#        aes(x = mds1, y = mds2, color = as.factor(group))) +
#   geom_point() +
#   geom_text(aes(label = id))

# cluster_result %>% filter(group==1)
# cluster_result %>% filter(group==2)
# cluster_result %>% filter(group==3)
# cluster_result %>% filter(group==4)

  #x = ~mds1.hod, y = ~ mds2.hod, text = ~customer_id
```
```{r heatmap-hod}

@@

data_heatmap_hod %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id,
                  fill = as.factor(group)),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) + theme_characterisation() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))
```

@@

moy_group <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

@@

data_heatmap_wkndwday_group <- quantile_gran(data_group,
                                  gran1="wknd_wday",
                                  quantile_prob_val = c(0.1, 0.25, 0.5, 0.75, 0.9),
                                  group="group") %>%
  pivot_wider(names_from = quantiles, values_from = quantiles_values)

wkndwday_group <- data_heatmap_wkndwday_group %>%
  ggplot(aes(x = category)) +
  geom_ribbon(aes(ymin = `25%`,
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
    geom_ribbon(aes(ymin = `10%`,
                  ymax = `90%`, group=group, fill = as.factor(group)), alpha = 0.4) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group,
             scales = "free_y",
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
    xlab("wknd-wday") +
  ylab("demand (in Kwh)") + theme_characterisation() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))

# wkndwday_group <- data_group %>% create_gran("wknd_wday") %>% 
#   ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
#   #lvplot::geom_lv(aes(fill = as.factor(group))) +
#   geom_boxplot(aes(fill = as.factor(group))) +
#   #ggridges::geom_density_ridges2(aes(x = general_supply_kwh, y = wknd_wday,fill = as.factor(group))) + coord_flip() +
# #geom_boxplot(aes(fill = as.factor(group))) +
#   #scale_fill_lv() +
#  xlab("wknd-wday") + 
#   ylab("demand (in Kwh)") +
#    facet_wrap(~group, 
#              #scales = "free_y", 
#              labeller = "label_value",
#              nrow = 4)+
#   theme_bw() +
#    theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank()) + 
#   theme(panel.spacing =unit(0, "lines")) + 
#   theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
#   scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey")) + 
#   theme(legend.position = "bottom") +
#   theme(panel.spacing =unit(0, "lines")) + 
#   theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))

@@

group <- f%>% hclust (method = "ward.D") %>% cutree(k=4)

@@

mds  = cmdscale(f)
rownames(mds) = id
colnames(mds) = c("mds1", "mds2")

@@

@@

```{r parcoord"}
parcoord
```

@@

moy_group_wpd <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) + theme_light() + 
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

@@

wkndwday_group_wpd <- data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
    xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))+ scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) + theme_light() + 
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

```{r combined-wpd"}

@@

>>>>

```{r mytheme}
theme_characterisation <- function() {

  theme_bw() + # seeting theme
    theme(strip.text = element_text(size = 9,
                                    margin = margin(b = 0, t = 0))) + # narrow facet space
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + # no axis ticks 
  theme(panel.spacing =unit(0, "lines")) +  # to ensure no gap between facets
    theme(axis.text.x = element_text(angle=90, hjust=1, size = 9)) + # rotate the x-axis text
    theme(legend.position = "bottom")+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  theme(axis.text.x = element_text(size=5))
}
```

```{r anchor}
anchor1 <- 11156027
anchor2 <- 10420683
anchor3 <- 8629763
anchor4 <- 11013154
kopt <- 4 # number of clusters
```

_Where they lie on the mds plot of total, hod, moy, wkndwday and wpd_

```{r data-read}

@@

hod <- read_rds(here("data/dist_gran_hod_356cust_robust.rds"))

distance <- wkndwday %>% 
  left_join(moy, by = c("item1", "item2")) %>% 
  left_join(hod, by = c("item1", "item2")) %>% 
  rename("wkndwday" ="distance.x",
         "moy" = "distance.y",
         "hod" = "distance") %>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2))) 
```

```{r data-pick}
total_distance <- distance %>% 
  #mutate(total = hod)
  mutate(total = wkndwday/2 + moy/12 + hod/24)

# 8454221 10420689 1001 8454221 10018298 10420689 9393696

# k-nearest neighbor pick function
nn_pick_function <- function(anchor, k = 5){
  data <- total_distance %>% filter(item1 %in% 
                            c(anchor)|item2 %in% 
                            c(anchor) ) %>% 
  #group_by(item1) %>%
  arrange(total) %>% 
  head(k) %>% 
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2)))

  unique(c(data$item1,data$item2)) %>% as_tibble()
}

data_pick_one <- nn_pick_function(anchor1)
data_pick_two <- nn_pick_function(anchor2)
data_pick_three <- nn_pick_function(anchor3)
data_pick_four <- nn_pick_function(anchor4)

# c(11013154, 9345642, 8328008, 8636035,8627007,8454235)

data_pick_cust <- bind_rows(
data_pick_one, data_pick_two, data_pick_three, data_pick_four,
.id = "design")

@@

data_pick <- read_rds(here::here("data/elec_nogap_2013_clean_356cust.rds"))%>%
  filter(customer_id %in% data_pick_cust$value) %>% 
  gracsr::scale_gran(method = "robust", response = "general_supply_kwh")
```

```{r mds-plots}

data_pick_char <- data_pick_cust %>% 
  rename("customer_id" = "value") %>% 
  mutate(customer_id = as.character(customer_id))

mds_all <- read_rds(here("data/mds_all.rds"))  %>% 
  left_join(data_pick_char)

highlight_df <- mds_all %>% filter(customer_id %in% data_pick_char$customer_id)

total_plot <- ggplot(mds_all,
aes(x = mds1.total, y = mds2.total)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.total, y = mds2.total, color = as.factor(design)), size = 2)

wpd_plot <- ggplot(mds_all,
aes(x = mds1.wpd, y = mds2.wpd)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.wpd, y = mds2.wpd, color = as.factor(design)), size = 2)

hod_plot <- ggplot(mds_all,
aes(x = mds1.hod, y = mds2.hod)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.hod, y = mds2.hod, color = as.factor(design)), size = 2)

moy_plot <- ggplot(mds_all,
aes(x = mds1.moy, y = mds2.moy)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x = mds1.moy, y = mds2.moy, color = as.factor(design)), size = 2)

wkndwday_plot <- ggplot(mds_all,
aes(x = mds1.wkndwday, y = mds2.wkndwday)) +
  geom_point(alpha = 0.3) +
  geom_point(data = highlight_df, 
             aes(x =  mds1.wkndwday, 
                 y =  mds2.wkndwday, 
                 color = as.factor(design)),
             size = 2)

p <- (total_plot + wpd_plot)/(hod_plot + moy_plot + wkndwday_plot)

p* +
  plot_layout(guides = "collect")

@@

group <- f %>% hclust (method = "ward.D") %>% cutree(k=kopt)

@@

mds  = cmdscale(f)
rownames(mds) = id
colnames(mds) = c("mds1", "mds2")
```

```{r heatmap-hod}

@@

data_heatmap_hod %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id,
                  fill = as.factor(group)),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) + theme_characterisation() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_x_discrete(breaks = seq(0, 23, 3))
# + scale_y_continuous(breaks = NULL) 
```

@@

moy_group <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_characterisation() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))
```

@@

wkndwday_data<- data_group %>% create_gran("wknd_wday") 
ylim1 = boxplot.stats(wkndwday_data$general_supply_kwh)$stats[c(1, 5)]

wkndwday_group <- wkndwday_data%>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  lvplot::geom_lv(aes(fill = as.factor(group), color = as.factor(group)), k=5, alpha = 0.5) +
  #geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)  +
  theme_characterisation() +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00", "grey"))

@@

group <- f%>% hclust (method = "ward.D") %>% cutree(k=kopt)

@@

# mds plot

# mds  = cmdscale(f)
# rownames(mds) = id
# colnames(mds) = c("mds1", "mds2")

@@

# will give error if you have got just one observation in a cluster

# ggplot(data = data_pcp,
#        aes(x = month_year, y = wkndwday)) +
#   geom_point() +
#   geom_text(aes(label = id))

@@

```{r parcoord}
parcoord
```

@@

moy_group_wpd <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

@@

wkndwday_group_wpd <- data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
    xlab("wknd-wday") + 
  ylab("demand (in Kwh)") + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)

wkndwday_data<- data_group %>% create_gran("wknd_wday") 
ylim1 = boxplot.stats(wkndwday_data$general_supply_kwh)$stats[c(1, 5)]

wkndwday_group_wpd <- wkndwday_data%>% 
  ggplot(aes(x=wknd_wday, y = general_supply_kwh)) +
  lvplot::geom_lv(aes(fill = as.factor(group), color = as.factor(group)), k=5, alpha = 0.5) +
  #geom_boxplot(aes(fill = as.factor(group), color = as.factor(group)),alpha = 0.5)+
  #geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim1*1.05)+
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)   + 
  theme_light()+ 
  theme_characterisation() +
 scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) 
```

```{r combined-wpd}

@@

```
```{r extra}
# total
# data = mds_total %>% left_join(data_pick_char)
# 
# highlight_df <- data %>% filter(customer_id%in% data_pick_char$customer_id)
#   
# total_plot <- ggplot(data,
# aes(x = mds1.total, y = mds2.total)) +
#   geom_point(alpha = 0.3) +
#   geom_point(data = highlight_df, 
#              aes(x = mds1.total, y = mds2.total, color = as.factor(design)), size = 2)
# 
# #hod
# 
# data = mds_hod %>% left_join(data_pick_char)
# 
# highlight_df <- data %>% filter(customer_id%in% data_pick_char$customer_id)
#   
# hod_plot <- ggplot(data,
# aes(x = mds1.hod, y = mds2.hod)) +
#   geom_point(alpha = 0.3) +
#   geom_point(data = highlight_df, 
#              aes(x = mds1.hod, y = mds2.hod, color = as.factor(design)), size = 2)+theme(legend.position = "bottom")
# 
# # moy
# 
# data = mds_moy %>% left_join(data_pick_char)
# 
# highlight_df <- data %>% filter(customer_id%in% data_pick_char$customer_id)
#   
# moy_plot <- ggplot(data,
# aes(x = mds1.moy, y = mds2.moy)) +
#   geom_point(alpha = 0.3) +
#   geom_point(data = highlight_df, 
#              aes(x = mds1.moy, y = mds2.moy, color = as.factor(design)), size = 2)+theme(legend.position = "bottom")
# 
# # wkndwday
# 
# data = mds_wkndwday %>% left_join(data_pick_char)
# 
# highlight_df <- data %>% filter(customer_id %in% data_pick_char$customer_id)
#   
# wkndwday_plot <- ggplot(data,
# aes(x = mds1.wkndwday, y = mds2.wkndwday)) +
#   geom_point(alpha = 0.3) +
#   geom_point(data = highlight_df, 
#              aes(x =  mds1.wkndwday, 
#                  y =  mds2.wkndwday, 
#                  color = as.factor(design)),
#              size = 2)+ theme(legend.position = "bottom")

### 2021-10-18 main.Rmd
adding new simulation files

<!-- grouping probability distributions across a harmony. This clustering algorithm is adopted to remove or appropriately adjust for auto correlation and unequal length in the data. The method could be further extended by clustering probability distributions conditional on one or more cyclic granularities. The following are some of the advantages of our proposed method. --

@@

    **Handling trend, seasonality, non-stationarity and auto-correlation:** Trend and seasonality are fundamental characteristics of time series data, and it is reasonable to define a time series according to its degree of trend and seasonality. These characteristics of the time series are lost or handled independently by considering probability distributions ( trend is lost) across categories of cyclic granularities (by independently modeling all seasonal fluctuations), and so there is no need to de-trend or de-seasonalize the data before conducting the clustering method. There is no need to omit holiday or weekend patterns for similar reasons.

    **Data transformation:** Robust scaling method is used before computing the Inter-category distances and NQT is built-in transformation used for computation of $wpd$, which forms the basis of Intra-category distances.

>>>>

<!-- grouping probability distributions across a harmony. This clustering algorithm is adopted to remove or appropriately adjust for auto correlation and unequal length in the data. The method could be further extended by clustering probability distributions conditional on one or more cyclic granularities. The following are some of the advantages of our proposed method. -->

@@

<!--Handling trend, seasonality, non-stationarity and auto-correlation:** Trend and seasonality are fundamental characteristics of time series data, and it is reasonable to define a time series according to its degree of trend and seasonality. These characteristics of the time series are lost or handled independently by considering probability distributions ( trend is lost) across categories of cyclic granularities (by independently modeling all seasonal fluctuations), and so there is no need to de-trend or de-seasonalize the data before conducting the clustering method. There is no need to omit holiday or weekend patterns for similar reasons-->

    **Data transformation:** Both robust scaling method and NQT are used before computing the JS-based distances and NQT is built-in transformation used for computation of $wpd$, which forms the basis of wpd-based distances.

    Robust scaling would keep the distribution intact

Normal-Quantile transform will transform the positively and negatively skewed distribution to a similar bell-shaped. From the transformed distribution, it is difficult to understand that raw distribution was of which shape. Also, multimodality gets hidden or magnitude get reversed with NQT. But deciles from the distribution will move in a similar manner as the raw distribution and hence the final distance matrix seem to be unaffected. Hence, this could be used. Also, practically most problems will have a very skewed distribution, it is often helpful to bring them to a normal-like shape before clustering.

### 2021-10-18 supplementary/distance-computation/real-data/04handpick-from356-mds.Rmd
adding new simulation files

```{r mds-all}
mds_all <- mds_hod %>% 
  left_join(mds_moy, by = "customer_id") %>% 
  left_join(mds_wkndwday, by = "customer_id") %>% 
  left_join(mds_total, by = "customer_id") %>% 
  left_join(mds_wpd, by = "customer_id") %>% 
  select(customer_id, everything())
```

>>>>

```{r mds-all}
mds_all <- mds_hod %>% 
  left_join(mds_moy, by = "customer_id") %>% 
  left_join(mds_wkndwday, by = "customer_id") %>% 
  left_join(mds_total, by = "customer_id") %>% 
  left_join(mds_wpd, by = "customer_id") %>% 
  select(customer_id, everything())

write_rds(mds_all, here("data/mds_all.rds"))
```
